Supplementary Materials: Introductory Physics Labs: A Tale of Two Transformations

### 2022-04-13 supplement/supplement.tex
Unmasked the supplement for the TPT article.

% \author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
% 5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
% \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
% street, Greenville, NC 27858 USA}

\author{First Author} \affiliation{Masked Institution}

\author{Second Author} \affiliation{Masked Institution}

@@

Labs are supervised by Author 2, but each section is run by Graduate TAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.

>>>>

\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
  5\textsuperscript{th} street, Greenville, NC 27858 USA}

\author{Mark W.\ Sprague} \affiliation{East Carolina University Department of Physics 1000 E.\
  5\textsuperscript{th} street, Greenville, NC 27858 USA}

% \author{First Author} \affiliation{Masked Institution}

% \author{Second Author} \affiliation{Masked Institution}

@@

Labs are supervised by Author 2, but each section is run by Graduate TAs (GTAs). The
transformed curriculum was jointly written by both of the authors.  GTA training was greatly
enhanced when the new lab curriculum was put in place.  Both authors, along with colleagues in
Biology and Chemistry, run a training for all GTAs in Biology, Chemistry, Geology, and Physics
as these disciplines are all using the same curricular format for their labs.  Author 2 runs a
weekly prep meeting with the GTAs, and Author 1 and the research team have supervised various
aspects of the transformation especially important for research such as curricular
implementation \citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.
